# Data 

## Sources

```{r include=FALSE}
library(readr)
download.file("https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/NHIS/2021/adult21csv.zip", destfile = "adult21.zip")
download.file("https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/NHIS/2020/adult20csv.zip", destfile="adult20.zip")
download.file("https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/NHIS/2019/adult19csv.zip", destfile="adult19.zip")
download.file("https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/NHIS/2018/samadultcsv.zip", destfile="adult18.zip")
data2021 <- unzip("adult21.zip")
data2020 <- unzip("adult20.zip")
data2019 <- unzip("adult19.zip")
data2018 <- unzip("adult18.zip")
NHIS_2021 <- readr::read_csv("adult21.csv", show_col_types = FALSE)
NHIS_2020 <- readr::read_csv("adult20.csv", show_col_types = FALSE)
NHIS_2019 <- readr::read_csv("adult19.csv", show_col_types = FALSE)
NHIS_2018 <- readr::read_csv("samadult.csv", show_col_types = FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(tibble)
library(forcats)
library(vcdExtra)
library(redav)
library(GGally)
library(ggalluvial)
NHIS_2019 <- select(NHIS_2019, c('ANXEV_A', 'AGEP_A', 'MARITAL_A', 'SEX_A', 'HISPALLP_A', 'ORIENT_A', 'REGION', 'SMKNOW_A', 'EMPWRKLSWK_A', 'PAIFRQ3M_A', 'CHDEV_A', 'CANEV_A', 'STREV_A', 'DIBEV_A', 'ASEV_A'))

NHIS_2020 <- select(NHIS_2020, c('ANXEV_A', 'AGEP_A', 'MARITAL_A', 'SEX_A', 'HISPALLP_A', 'ORIENT_A', 'REGION', 'SMKNOW_A', 'EMPWRKLSWK_A', 'PAIFRQ3M_A', 'CHDEV_A', 'CANEV_A', 'STREV_A', 'DIBEV_A', 'ASEV_A'))

NHIS_2021 <- select(NHIS_2021, c('ANXEV_A', 'AGEP_A', 'MARITAL_A', 'SEX_A', 'HISPALLP_A', 'ORIENT_A', 'REGION', 'SMKNOW_A', 'EMPWRKLSW1_A', 'PAIFRQ3M_A', 'CHDEV_A', 'CANEV_A', 'STREV_A', 'DIBEV_A', 'ASEV_A'))

col_names = c("History_of_Anxiety", "Age", "Marital_Status", "Sex", "Race", "Sexual_Orientation", "Region", "Smoking", "Employment", "Chronic_pain", "History_of_Heart_disease", "History_of_Cancer", "History_of_Stroke", "History_of_Diabetes", "History_of_Asthma")

colnames(NHIS_2019) <- col_names
colnames(NHIS_2020) <- col_names
colnames(NHIS_2021) <- col_names
```


```{r}
data_cleaner <- function(df, year,Covid){
  df_test <- df
  
  df_test$Year <- year
  df_test$Covid_Year <- Covid
  
  #df_test[is.na(df_test)] = 'Missing'
  
  df_test <- subset(df_test, Age>=18 & Age <= 65)
  
  df_test <- df_test %>% mutate_at(
                  c('History_of_Anxiety','History_of_Heart_disease','History_of_Cancer','History_of_Stroke',
                    'History_of_Diabetes','History_of_Asthma','Employment'),  ~ case_when(
                                          . == 1 ~ "Yes",
                                          . == 2 ~ "No",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"))
  df_test <- df_test%>% mutate_at(
                  c('Marital_Status'),  ~ case_when(
                                          . == 1 ~ "Married",
                                          . == 2 ~ "Unmarried",
                                          . == 3 ~ "Unmarried",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"))
  df_test <- df_test%>% mutate_at(
                  c('Sex'),  ~ case_when(
                                          . == 1 ~ "Male",
                                          . == 2 ~ "Female",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"))

  df_test <- df_test%>% mutate_at(
                  c('Race'),  ~ case_when(
                                          . == 02 ~ "White",
                                          . == 03 ~ "Black",
                                          . == 04 ~ "Asian",
                                          . == 01 ~ "Others",
                                          . == 05 ~ "Others",
                                          . == 06 ~ "Others",
                                          . == 07 ~ "Others",
                                          . == 97 ~ "Refused",
                                          . == 98 ~ "Do not know",
                                          . == 99 ~ "Do not know",
                                          TRUE ~ "Missing"
                                        ))
  df_test <- df_test %>% mutate_at(
                  c('Sexual_Orientation'),  ~ case_when(
                                          . == 1 ~ "Gay_Lesbian",
                                          . == 2 ~ "Straight",
                                          . == 3 ~ "Bisexual",
                                          . == 4 ~ "Others",
                                          . == 5 ~ "Others",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"
                                        ))
  df_test <- df_test%>% mutate_at(
                  c('Region'),  ~ case_when(
                                          . == 1 ~ "Northeast",
                                          . == 2 ~ "Midwest",
                                          . == 3 ~ "South",
                                          . == 4 ~ "West",
                                          TRUE ~ "Missing"
                                        ))
  df_test <- df_test%>% mutate_at(
                  c('Chronic_pain'), ~ case_when(
                                          . == 1 ~ "Never",
                                          . == 2 ~ "Some days",
                                          . == 3 ~ "Most days",
                                          . == 4 ~ "Every day",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"
                                        ))
    df_test <- df_test%>% mutate_at(
                  c('Smoking'),  ~ case_when(
                                          . == 1 ~ "Every day",
                                          . == 2 ~ "Some days",
                                          . == 3 ~ "Not at all",
                                          . == 7 ~ "Refused",
                                          . == 8 ~ "Do not know",
                                          . == 9 ~ "Do not know",
                                          TRUE ~ "Missing"
                                        ))

  return(df_test)
}
```


```{r}
NHIS_2019_test = data_cleaner(NHIS_2019,year = 2019,Covid='No')
NHIS_2020_test = data_cleaner(NHIS_2020,year = 2020,Covid='Yes')
NHIS_2021_test = data_cleaner(NHIS_2021,year = 2021,Covid='Yes')
```


```{r}
df <- select(NHIS_2018, c('AFLHCA17', 'AGE_P', 'R_MARITL', 'SEX', 'MRACRPI2', 'ASISIM', 'ASISIF', 'REGION', 'SMKNOW', 'DOINGLWA', 'PAIN_2A', 'CHDEV', 'CANEV', 'STREV', 'DIBEV1', 'AASMEV'))

colnames(df) <- c("History_of_Anxiety", "Age", "Marital_Status", "Sex", "Race", "Sexual_Orientation_Male", "Sexual_Orientation_Female", "Region", "Smoking", "Employment", "Chronic_pain", "History_of_Heart_disease", "History_of_Cancer", "History_of_Stroke", "History_of_Diabetes", "History_of_Asthma")
df$Year <- 2018
df$Covid_Year <- 'No'
df$Sexual_Orientation <- coalesce(df$Sexual_Orientation_Male, df$Sexual_Orientation_Female)
df <- subset (df, select = -c(Sexual_Orientation_Male, Sexual_Orientation_Female))
df <- subset(df, Age>=18 & Age <= 65) 

df1 <- df%>%
  mutate(
    History_of_Anxiety = case_when(df$History_of_Anxiety == 1 ~ 'Yes', df$History_of_Anxiety == 2 ~ 'No',
                                   df$History_of_Anxiety == 7 ~ "Refused",
                              df$History_of_Anxiety == 8 ~ "Do not know",
                              df$History_of_Anxiety == 9 ~ "Do not know",
                        TRUE ~ 'Missing'),
    Marital_Status = case_when(df$Marital_Status == 1 | df$Marital_Status == 2 | df$Marital_Status == 3 ~ 'Married',
                               df$Marital_Status == 0 | df$Marital_Status == 4 | df$Marital_Status == 5 | df$Marital_Status == 6 | df$Marital_Status == 7 |  df$Marital_Status == 8 ~ 'Unmarried',
                                          df$Marital_Status == 9 ~ "Do not know",
                               TRUE ~ 'Missing'),
    Race = case_when(df$Race == 1 ~ 'White',
                     df$Race == 2 ~ 'Black',
                     df$Race == 9 | df$Race == 10 | df$Race == 11 | df$Race == 15 ~ 'Asian',
                     df$Race == 3 ~ 'Others',
                     TRUE ~ 'Missing'),
    Smoking = case_when(df$Smoking == 1 ~ "Every day",
                        df$Smoking == 2 ~ "Some days",
                        df$Smoking == 3 ~ "Not at all",
                        df$Smoking == 7 ~ "Refused",
                        df$Smoking == 8 ~ "Do not know",
                        df$Smoking == 9 ~ "Do not know",
                        TRUE ~ 'Missing'),
    Sex = case_when(df$Sex == 1 ~ 'Male', df$Sex == 2 ~ 'Female', 
                         TRUE ~ 'Missing'),
    Sexual_Orientation = case_when(df$Sexual_Orientation == 1 ~ 'Gay_Lesbian',
                          df$Sexual_Orientation == 2 ~ 'Straight',
                          df$Sexual_Orientation == 3 ~ 'Others',
                          TRUE ~ 'Missing'),
    Employment = case_when(df$Employment == 1 | df$Employment == 2 | df$Employment == 4 ~ 'Yes',
                           df$Employment == 3 | df$Employment == 5 ~ 'No',
                          df$Employment == 7 ~ "Refused",
                        df$Employment == 8 ~ "Do not know",
                        df$Employment == 9 ~ "Do not know",
                           TRUE ~ 'Missing'),
    Region = case_when(df$Region == 1 ~ 'Northeast',
                       df$Region == 2 ~ 'Midwest',
                       df$Region == 3 ~ 'South',
                       df$Region == 4 ~ 'West',
                       TRUE ~ 'Missing'),
    Chronic_pain = case_when(df$Chronic_pain == 1 ~ 'Never',
                             df$Chronic_pain == 2 ~ 'Some days',
                             df$Chronic_pain == 3 ~ 'Most days',
                             df$Chronic_pain == 4 ~ 'Every day',
                             df$Chronic_pain== 7 ~ "Refused",
                              df$Chronic_pain == 8 ~ "Do not know",
                              df$Chronic_pain == 9 ~ "Do not know",
                             TRUE ~ 'Missing'),
    History_of_Heart_disease = case_when(df$History_of_Heart_disease == 1 ~ 'Yes',
                              df$History_of_Heart_disease == 2 ~ 'No',
                              df$History_of_Heart_disease== 7 ~ "Refused",
                              df$History_of_Heart_disease == 8 ~ "Do not know",
                              df$History_of_Heart_disease == 9 ~ "Do not know",
                              TRUE ~ 'Missing'),
    History_of_Cancer = case_when(df$History_of_Cancer == 1 ~ 'Yes',
                              df$History_of_Cancer == 2 ~ 'No',
                              df$History_of_Cancer == 7 ~ "Refused",
                              df$History_of_Cancer == 8 ~ "Do not know",
                              df$History_of_Cancer == 9 ~ "Do not know",
                              TRUE ~ 'Missing'),
    History_of_Stroke  = case_when(df$History_of_Stroke  == 1 ~ 'Yes',
                              df$History_of_Stroke == 2 ~ 'No',
                              df$History_of_Stroke == 7 ~ "Refused",
                              df$History_of_Stroke == 8 ~ "Do not know",
                              df$History_of_Stroke == 9 ~ "Do not know",
                              TRUE ~ 'Missing'),
    History_of_Diabetes = case_when(df$History_of_Diabetes  == 1 ~ 'Yes',
                              df$History_of_Diabetes == 2 ~ 'No',
                              df$History_of_Diabetes == 7 ~ "Refused",
                              df$History_of_Diabetes == 8 ~ "Do not know",
                              df$History_of_Diabetes == 9 ~ "Do not know",
                              TRUE ~ 'Missing'),
    History_of_Asthma = case_when(df$History_of_Asthma  == 1 ~ 'Yes',
                              df$History_of_Asthma == 2 ~ 'No',
                              df$History_of_Asthma == 7 ~ "Refused",
                              df$History_of_Asthma == 8 ~ "Do not know",
                              df$History_of_Asthma == 9 ~ "Do not know",
                              TRUE ~ 'Missing')
    )

NHIS_2018_test = df1
```

The data we use are from the National Health Interview Survey. It contains the results of interviews with about 30,000 people per year. The National Center for Health Surveys collects and processes the survey data. (hereafter referred to as NCHS) Each year, NCHS conducts a cross-sectional household interview survey of a specific population at a specific time through a geographic subgroup sampling technique. After the survey, they process the data, store it in a CSV file, and provide documentation that describes the meaning of each column and the keywords of the questions.

The NCHS website can find the survey data for each year from 1993 to 2021. We selected the recent four years of data for analysis. Since most of the questions interviewed in recent years were similar, we could easily find overlaps in the data and analyze them. Secondly, we also expected to know whether covid-19 is a factor that affects anxiety. Therefore, we selected data from two years before and two years after the pandemic. 

```{r}
NHIS_final <- rbind(NHIS_2019_test, NHIS_2020_test, NHIS_2021_test, NHIS_2018_test)
str(NHIS_final)
```

After the process of data cleanups, we have the data information shown in the figure above. The final data will contain 17 columns, with all categorical variables except for age. The most frequent values are yes or no, which is consistent with the characteristics of survey data. For each year of data, there are nearly 30,000 people, and we set the target group at 18 to 65 years old. So after filtering out other age groups, we end up with 84975 rows. 

Before we cleaned the data, we considered that there would be missing data as common sense dictates that respondents would not be forced to answer every question.  This also became apparent after we cleaned the data, as several columns had missing values, and not all answers were valuable.  Some people refuse to answer the questions or answers they don't know.  This could be a potential problem for the accuracy of our data.

## Cleaning / transformation

The data we are looking for on the official NCHS website is a compressed file ending in ".zip". In this case, we use the URL to read it. Then we unzip it to extract the CSV file. Since we will be using four years of data, this step needs to be repeated four times.

In the original document, each column corresponds to a survey question. Using the question as a column name is not practical because it is very long. Therefore, the column names in the file are labelled with a combination of letters and numbers. NCHS provides the documentation to help us understand each column's meaning and the corresponding survey question. Once we have confirmed the columns we need to use by searching for keywords, we use select to retrieve these columns from each year of data. We know the characteristics of each column, but the viewer may have yet to have the opportunity to read the documentation. Therefore, we need to change the names of the columns so that the viewer understands the values they are referring to. It will also be easier for us to use during the rest of the exploratory data analysis.

Next, we notice that the column values are labelled by the numbers 1, 2, 3, 4, etc. Just like the answers to the multiple-choice questions. So to convert the column values into easy-to-read text, we open the documentation again, which indicates the answer for each number. By using mutate, we converted each column's values into easy-to-understand words. After this cleaning of the data, we can start the subsequent analysis.

## Missing value analysis
```{r fig.width=22, fig.height=10}
NHIS_Missing <- NHIS_final %>%
  select("History_of_Anxiety", "Smoking","Age", "Marital_Status", "Sex", "Race", "Sexual_Orientation", "Region", "Employment", "Chronic_pain", "History_of_Heart_disease", "History_of_Cancer", "History_of_Stroke", "History_of_Diabetes", "History_of_Asthma") %>%
  mutate(History_of_Anxiety = na_if(History_of_Anxiety, "Missing")) %>%
  mutate(Age = na_if(Age, "Missing")) %>%
  mutate(Marital_Status = na_if(Marital_Status, "Missing")) %>%
  mutate(Sex = na_if(Sex, "Missing")) %>%
  mutate(Race = na_if(Race, "Missing")) %>%
  mutate(Smoking= na_if(Smoking, "Missing")) %>%
  mutate(Sexual_Orientation = na_if(Sexual_Orientation, "Missing")) %>%
  mutate(Region = na_if(Region, "Missing")) %>%
  mutate(Employment = na_if(Employment, "Missing")) %>%
  mutate(Chronic_pain = na_if(Chronic_pain, "Missing")) %>%
  mutate(History_of_Heart_disease = na_if(History_of_Heart_disease, "Missing")) %>%
  mutate(History_of_Cancer = na_if(History_of_Cancer, "Missing")) %>%
  mutate(History_of_Stroke = na_if(History_of_Stroke, "Missing")) %>%
  mutate(History_of_Diabetes = na_if(History_of_Diabetes, "Missing")) %>%
  mutate(History_of_Asthma = na_if(History_of_Asthma, "Missing"))

plot_missing(NHIS_Missing, percent = FALSE)
```

The data we use is based on the interviewer's responses. Because of the interview data and the fact that it is not mandatory to answer each question, we have values for many questions that are missing. That is, the interviewees chose not to answer the question. With four years of data, we will deal with a large portion of missing values. We tried to use a heatmap to visualize the missing values in rows and columns, but because of the large amount of data. It is not possible to plot the whole graph. So we chose to use plot_missing() from redav to help us see if there are any patterns hidden in these missing values.

Based on the results above, we can see that for the more basic personal information such as age, gender and region. The interviewees are willing to choose to answer. This is not difficult to understand, as we mentioned that each year's interview population was randomly selected through a geographic subgroup sampling technique. The area of residence of the popular respondents at the time of the interview was also not non-disclosed. In the case of the more personal questions about personal health and sexual orientation, there are a large number of missing values. Therefore, we can see that the interviewees are still more concerned about their privacy. This also reflects the uncertainty of the data we use. The missing values of columns show that the overlap of the Smoking, History of Anxiety, and Sexual Orientation columns is slightly relatively high. However, there is no obvious pattern. Therefore, there is no significant pattern of missing values in the dataset. 
