--- 
title: "NHIS Anxiety Analysis in Adults"
author: "Zhe Wang, Yingyi Zhu, Zixiao Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
--- 
title: "NHIS Anxiety Analysis in Adults"
author: "Zhe Wang, Yingyi Zhu, Zixiao Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction

In today’s rapidly developing society, it’s not surprising to find out that almost everyone feels certain degrees of anxiety. When it comes to work place, people can be facing high workloads and tight deadlines. When it comes to school, students might be experiencing peer pressure academically. When it comes to family, people are under pressure of taking responsibility consistently. When it comes to success, some might be concerned about the definition of success. All the above can be signs of anxiety, while anxiety is also manifested in a variety of mild or severe psychological diseases and behavioral symptoms. Therefore, as anxiety is closely related to us, we would like to explore the relationships of anxiety to other factors of our life, and if possible, what kind of information these relationships revealed to us.

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Proposal
## Research topic

  Occasional anxiety is a normal part of life. Being a student at Columbia University, it's not uncommon to hear phrases such as being stressed about school work, midterms, and career searching. One news [article](https://www.who.int/news/item/02-03-2022-covid-19-pandemic-triggers-25-increase-in-prevalence-of-anxiety-and-depression-worldwide) from the **World Health Organization** even revealed that the prevalence of anxiety and depression has increased by 25% globally during the social environment of the COVID-19 pandemic. Furthermore, anxiety may interfere with daily activities, such as work performance, schoolwork, and relationships. Physical symptoms can include rapid heartbeat, tremors, breathlessness, and other symptoms such as upset stomach or nausea.

  For this exploratory data project, our team will look at a four-year NHIS data on 18-65 aged adults, focusing on the relationship between anxiety and other general factors such as gender and employment. Moreover, we will further our analysis by looking at other health factors like heart disease that could be correlated with feelings of anxiety.

## Data availability
  The [National Health Interview Survey](https://www.cdc.gov/nchs/nhis/data-questionnaires-documentation.htm)
 data we utilized was collected and processed by the National Center for Health
Statistics (NCHS). It is a cross-sectional household interview survey conducted through a geographic subgroup sampling technique (random selection), updated annually. The data contains statistical information on the interviewer's health status, health-related behaviors, and healthcare utilization history since 1993.

  We will limit our analysis to the recent years, 2018-2021 survey data only, and within the group
of 18-65 aged adults. The sample adult population of each year would be approximately 30,000. The data format we will be using will be CSV format. The total size over the four years adults data would be 112MB, including elders, which we would feature engineer later to exclude. We intended to import the CSV files to R studios by used the built-in read.csv(...) function call to conduct data cleaning and visualization of the relationship of anxiety between the following factors that were found in all four years of surveys: 

  For common independent factors, we have ages, years (split to Covid/non-Covid), marital status,
genders, races, sexual orientations, household numbers, regions, habits (such as smoking, alcohol, etc.), employment, history of chronic pains and hours of sleep. The list's order is random and does not have ranks of importance. We include these factors to help us understand our samples and the distribution of anxiety in the population, such as genders and regions. If the sample population distribution is highly imbalanced, we will thus adjust our strategies correspondingly by downsampling or upsampling.

  Additional to the common independent factors, we would further explore certain physical health
factors we found might be correlated: history of heart disease, history of cancer, history of stroke, history of diabetes, and history of asthma. Again, the order of the list above is random. We are interested in exploring the relationship between these above factors because many studies have shown mental health is correlated with physical health to different degrees. We would, therefore, like to examine the degree of correlation.

  One additional comment regarding our data is that it’s interview survey data, which are answered
without 100% truth guarantees. It’s possible the interviewees chose to give inaccurate information out of self-interest. Moreover, the health-related questions are also self-answered, which means there is not necessarily a formal background check to confirm. We don’t know if some health conditions have been cured. Therefore, we decided to use terms such as “history of anxiety” and “history of cancers” to adjust the level of accuracy.

  In summary, we will explore the relationship between anxiety(self-indicated or formally
diagnosed) with other factors, such as age, gender, and years, with a further focus on physical conditions. The NHIS data will help us achieve a four-year exploration with a rich sample adult population of around 30,000 each year. We will keep in mind the inaccuracy that comes with the nature of the NHIS data collection process.

Here is a link to the NHIS data: 
[National Health Interview Survey](https://www.cdc.gov/nchs/nhis/data-questionnaires-documentation.htm)

<!--chapter:end:proposal.Rmd-->


# Data 

Placeholder


## Sources
## Cleaning / transformation
## Missing value analysis

<!--chapter:end:data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

```{r}
library(dplyr)
library(tidyr)
library(grid)
library(ggplot2)
library(GGally)
library(ggalluvial)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

## Female vs Male, which group are more sensitive to anxiety?
```{r}
options(dplyr.summarise.inform = FALSE)
nhisBar <- NHIS_final %>%
  filter(History_of_Anxiety !='Missing') %>%
  filter(Sex=="Male" | Sex=="Female")
nhisBar1 <- nhisBar %>%
  group_by(Year, History_of_Anxiety, Sex) %>%
  dplyr::summarise(Freq = n())
ggplot(nhisBar1, aes(x = Year, y=Freq, fill = History_of_Anxiety)) + 
    geom_bar(position="fill", stat="identity") +
  facet_wrap(~Sex) +
  scale_fill_manual(values = c("#FAE367", "#768CCe", "#E7BCC6", "#B4BBC0"), limits = c("Yes", "No", "Refused", "Do not know")) +
  theme_minimal()
```

Since the population interviewed each year was not a fixed group of people, we have no way of knowing whether the same group of people had a change in their mental health during those years. However, according to the graph above, the percentage of interviewees with history of anxiety has increased yearly—both the percentage of males and females. On the male side, we can see that the increase is relatively small, but there is no sign of a decrease. On the female side, we can see a significant increase from 2018 to 2019, which is almost 50% of those with history of anxiety in 2018. Such increase continues each year slowly after that, and almost 25% of women are having history of anxiety by 2021. In summary, the proportion of women with history of anxiety is greater than that of men, with both indicates signs of continue increase.

```{r}
df <- NHIS_final
df$Freq <-1
df = df %>% filter(Marital_Status !='Missing')
df = df %>% filter(Sex !='Missing' & Sex != "Do not know" & Sex != "Refused")
df = df %>% filter(History_of_Anxiety !='Missing' & History_of_Anxiety != "Do not know" & History_of_Anxiety != "Refused")
df = df %>% filter(Employment !='Missing' & Employment != "Do not know")
df = df %>% filter(Race !='Missing')
df = df %>% filter(Covid_Year !='Missing')
df = df %>% filter(Region !='Missing' & Region!="Do not know" & Region != "Refused")
df = df %>% filter(History_of_Heart_disease !='Missing')
df = df %>% filter(History_of_Cancer !='Missing')
df = df %>% filter(History_of_Stroke !='Missing')
df = df %>% filter(Smoking !="Do not know" & Smoking != "Refused")
df = df %>% filter(Chronic_pain !="Do not know" & Chronic_pain!= "Refused")
df = df %>% filter(History_of_Diabetes !='Missing'  & History_of_Diabetes!="Do not know" & History_of_Diabetes != "Refused")
df = df %>% filter(History_of_Asthma !='Missing')
df = df %>% filter(Sexual_Orientation !='Missing' & Sexual_Orientation !='Missing')
df <- df %>% mutate_at(
                c('Sexual_Orientation'),  ~ case_when(
                                        . == "Others" ~ "LGBT+",
                                        . == "Straight" ~ "Straight",
                                        TRUE ~ "Straight"
                                        ))

```


## Anxiety and Identity: The Intersection of Race and Sex
```{r}
options(dplyr.summarise.inform = FALSE)
df$Race  <- factor(df$Race,c('White','Others','Black','Asian') )
df$Race  <-as.ordered(df$Race)

counts2 <- df %>%
  group_by(Race,Sex,History_of_Anxiety) %>%
  summarize(Freq = sum(Freq))


vcd::mosaic(History_of_Anxiety ~ Sex + Race, counts2,
            direction = c("h", "v", "h"),
            highlighting_fill = icecreamcolors)
```

Anxiety among different genders still follows the pattern from the first plot, with females showing higher correlation with history of anxiety than males. However, if breaking down the data by race, we can see that females in the “other” category show a higher rate of anxiety than Black and Asian females, compared to males, which is interesting to find out. 

## The Burden of Chronic Pain: Exploring the Prevalence and Impact of Chronic Pain among sex
```{r fig.width=9, fig.height=5}
# alluvium plot
counts2 <- df %>%
  group_by(History_of_Anxiety,Chronic_pain,Sex) %>%
  summarize(Freq = sum(Freq))


ggplot(counts2, aes(axis = History_of_Anxiety, axis3 = Chronic_pain, axis2 = Sex,  y = Freq)) +
  geom_alluvium(aes(fill = History_of_Anxiety), width = 1/12) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = paste(after_stat(stratum), "\n", after_stat(count)))) +
  scale_x_discrete(limits = c("History_of_Anxiety", "Chronic_pain", "Smoking"))
```

Chronic pain is defined as pain that persists for more than three months and cannot be easily explained by any underlying medical condition. It can be caused by a variety of factors, including injuries, illnesses, and surgery. Chronic pain can have a significant impact on a person's physical and mental health, and can lead to a decreased quality of life. This graph is consistent with previous plots, which has found that women are more likely to experience chronic pain than men. Additionally, the graph shows that women are more likely to experience anxiety and chronic pain simultaneously. Overall, this graph highlights the importance of addressing anxiety and chronic pain in women, as they are more likely to experience these conditions.

## Anxiety vs Other Diseases: similarity in color patterns
```{r}
orderedclasses <- c("Yes", "No", "Refused", "Do not Know", "Missing")
mydata <- NHIS_final %>%
  select("History_of_Anxiety","History_of_Heart_disease")
mydata$History_of_Anxiety <- factor(mydata$History_of_Anxiety, levels = orderedclasses)
mydata$History_of_Heart_disease <- factor(mydata$History_of_Heart_disease, levels = orderedclasses)
mydata1 <- mydata %>%
  group_by(History_of_Anxiety, History_of_Heart_disease) %>%
  dplyr::summarise(Freq=n()) 
mydata1 <- mydata1 %>% group_by(History_of_Anxiety) %>% 
  mutate(Total = sum(Freq)) %>% ungroup()

mydata2 <- NHIS_final %>%
  select("History_of_Anxiety","History_of_Cancer")
mydata2$History_of_Anxiety <- factor(mydata2$History_of_Anxiety, levels = orderedclasses)
mydata2$History_of_Cancer <- factor(mydata2$History_of_Cancer, levels = orderedclasses)
mydata3 <- mydata2 %>%
  group_by(History_of_Anxiety, History_of_Cancer) %>%
  dplyr::summarise(Freq=n()) 
mydata3 <- mydata3 %>% group_by(History_of_Anxiety) %>% 
  mutate(Total = sum(Freq)) %>% ungroup()

mydata4 <- NHIS_final %>%
  select("History_of_Anxiety","History_of_Stroke")
mydata4$History_of_Anxiety <- factor(mydata4$History_of_Anxiety, levels = orderedclasses)
mydata4$History_of_Stroke <- factor(mydata4$History_of_Stroke, levels = orderedclasses)
mydata5 <- mydata4 %>%
  group_by(History_of_Anxiety, History_of_Stroke) %>%
  dplyr::summarise(Freq=n()) 
mydata5 <- mydata5 %>% group_by(History_of_Anxiety) %>% 
  mutate(Total = sum(Freq)) %>% ungroup()
```

```{r}
mydata6 <- NHIS_final %>%
  select("History_of_Anxiety","History_of_Diabetes")
mydata6$History_of_Anxiety <- factor(mydata6$History_of_Anxiety, levels = orderedclasses)
mydata6$History_of_Diabetes <- factor(mydata6$History_of_Diabetes, levels = orderedclasses)
mydata7 <- mydata6%>%
  group_by(History_of_Anxiety, History_of_Diabetes) %>%
  dplyr::summarise(Freq=n()) 
mydata7 <- mydata7 %>% group_by(History_of_Anxiety) %>% 
  mutate(Total = sum(Freq)) %>% ungroup()
```

```{r}
mydata8 <- NHIS_final %>%
  select("History_of_Anxiety","History_of_Asthma")
mydata8$History_of_Anxiety <- factor(mydata8$History_of_Anxiety, levels = orderedclasses)
mydata8$History_of_Asthma <- factor(mydata8$History_of_Asthma, levels = orderedclasses)
mydata9 <- mydata8%>%
  group_by(History_of_Anxiety, History_of_Asthma) %>%
  dplyr::summarise(Freq=n()) 
mydata9 <- mydata9 %>% group_by(History_of_Anxiety) %>% 
  mutate(Total = sum(Freq)) %>% ungroup()
```


```{r fig.width=9, fig.height=8}
h1 <- ggplot(subset(subset(mydata1, !is.na(History_of_Heart_disease)), !is.na(History_of_Anxiety)), aes(x = History_of_Anxiety, y = History_of_Heart_disease)) +
  geom_tile(aes(fill = (Freq/Total)), color = "white") +
  coord_fixed() + 
  scale_fill_gradientn(colors=c("#aacfe5", "#3888c0", "#08336e"))+
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1))+
  labs(fill = "Freq in Anxiety")

h2 <- ggplot(subset(subset(mydata3, !is.na(History_of_Cancer)), !is.na(History_of_Anxiety)), aes(x = History_of_Anxiety, y = History_of_Cancer)) +
  geom_tile(aes(fill = (Freq/Total)), color = "white") +
  coord_fixed() + 
  scale_fill_gradientn(colors=c("#aacfe5", "#3888c0", "#08336e"))+
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1))+
  labs(fill = "Freq in Anxiety")

h3 <- ggplot(subset(subset(mydata5, !is.na(History_of_Stroke)), !is.na(History_of_Anxiety)), aes(x = History_of_Anxiety, y = History_of_Stroke)) +
  geom_tile(aes(fill = (Freq/Total)), color = "white") +
  coord_fixed() + 
  scale_fill_gradientn(colors=c("#aacfe5", "#3888c0", "#08336e"))+
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1))+
  labs(fill = "Freq in Anxiety")

h4 <- ggplot(subset(subset(mydata7, !is.na(History_of_Diabetes)), !is.na(History_of_Anxiety)), aes(x = History_of_Anxiety, y = History_of_Diabetes)) +
  geom_tile(aes(fill = (Freq/Total)), color = "white") +
  coord_fixed() + 
  scale_fill_gradientn(colors=c("#aacfe5", "#3888c0", "#08336e"))+
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1))+
  labs(fill = "Freq in Anxiety")

h5 <- ggplot(subset(subset(mydata9, !is.na(History_of_Asthma)), !is.na(History_of_Anxiety)), aes(x = History_of_Anxiety, y = History_of_Asthma)) +
  geom_tile(aes(fill = Freq/Total), color = "white") +
  coord_fixed() + 
  scale_fill_gradientn(colors=c("#aacfe5", "#3888c0", "#08336e"))+
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1)) +
  labs(fill = "Freq in Anxiety")
gridExtra::grid.arrange(h1, h2, h3, h4,h5)
```

In the above five plots, we tried to find the proportion of responses for other diseases. The x-axis represents the population’s responses to the history of Anxiety breaking down by other diseases. The y-axis corresponds to the responses for other physical diseases. For example, the first graph contains information regarding history of anxiety and history of heart disease; among those who had history of anxiety, more than 75% chose no in history of heart disease, which means more than 75% of people do not have heart disease. 

After comparing Anxiety with other diseases, we can see that the percentage of people who answered yes to both asthma and a history of Anxiety is the highest among the five diseases, which can indicate a more positive relationship between the two compared to others. It’s also interesting to find out that all five physical diseases shown similar patterns by looking at the color. One possible reason can be people with other physical diseases might be affected by the concern of such disease therefore become anxious about their wellness.

## Deeper dive into relationship between anxiety and physical diseases

```{r}
nhisAnxiety <- NHIS_final %>%
  select(History_of_Anxiety, Year)
anxiety<-as.data.frame(table(NHIS_final$History_of_Anxiety))


nhisHeart <- NHIS_final %>%
  select(History_of_Heart_disease)
heart<-as.data.frame(table(NHIS_final$History_of_Heart_disease))

nhisCancer <- NHIS_final %>%
  select(History_of_Cancer)
cancer<-as.data.frame(table(NHIS_final$History_of_Cancer))

nhisStroke <- NHIS_final %>%
  select(History_of_Stroke)
stroke<-as.data.frame(table(NHIS_final$History_of_Stroke))

nhisDiabetes <- NHIS_final %>%
  select(History_of_Diabetes)
diabetes<-as.data.frame(table(NHIS_final$History_of_Diabetes))

nhisAsthma <- NHIS_final %>%
  select(History_of_Asthma)
asthma<-as.data.frame(table(NHIS_final$History_of_Asthma))
```

```{r}
heat1 <- inner_join(x=anxiety, y=heart, by="Var1")
heat2 <- inner_join(x=heat1, y=cancer, by="Var1")
heat3 <- inner_join(x=heat2, y=stroke, by="Var1")
heat4 <- inner_join(x=heat3, y=diabetes, by="Var1")
heat5 <- inner_join(x=heat4, y=asthma, by="Var1")
colnames(heat5)[1:7] =c("Answer", "Anxiety","Heart_disease", "Cancer", "Stroke", "Diabetes", "Asthma")
draw_biplot(heat5, points=FALSE)
```

The loading plots include vectors for each disease, including anxiety. We note that the vectors for anxiety disorders and asthma patients are relatively close. From our study of the biplot, we know that forming a small angle means that the two variables are positively correlated. Combining this with our findings in the previous heatmap, there is a link between anxiety and asthma. Second, we can also note that the angle between the history of anxiety and other disorders is between 75 and 100 degrees, which means they are not likely to be correlated.

## Geographic Link Between Diabetes and Anxiety
```{r}
# alluvium plot
counts2 <- df %>%
  group_by(History_of_Anxiety,Region,History_of_Diabetes) %>%
  summarize(Freq = sum(Freq))


ggplot(counts2, aes(axis = History_of_Anxiety, axis3 = Region, axis2 = History_of_Diabetes,  y = Freq)) +
  geom_alluvium(aes(fill = History_of_Anxiety), width = 1/12) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = paste(after_stat(stratum), "\n", after_stat(count)))) +
  scale_x_discrete(limits = c("History_of_Anxiety", "Region", "History_of_Diabetes"))
```

Diabetes is a chronic condition in which the body is unable to properly regulate blood sugar levels. This can lead to a range of complications, including damage to the heart, blood vessels, nerves, and kidneys. The plot you are referring to suggests that there might be a higher prevalence of diabetes in the southern region of the United States, and that people in this region are also more likely to experience anxiety.There are several potential reasons for this correlation. One possible explanation is that people who live in the southern region of the US may have different lifestyles and dietary habits that contribute to the development of diabetes and anxiety. For example, southern cuisine often includes high-fat and high-calorie dishes, which can increase the risk of obesity and related conditions.

## Are elderly people less anxious about their life?

```{r}

nhisCleve <- NHIS_final %>%
  filter(History_of_Anxiety !='Missing') 
nhisCleve$History_of_Anxiety <- factor(nhisCleve$History_of_Anxiety)
nhisCleve1 <- nhisCleve %>%
  group_by(Age, History_of_Anxiety) %>%
  dplyr::summarise(freq=n()) 
nhisCleve2 <- nhisCleve1%>%
  mutate(Total = sum(freq))
nhisCleve3 <- nhisCleve2%>%
  mutate(pro = freq/Total)
ggplot(nhisCleve3, aes(x = pro, y = Age)) +
 geom_point(aes(color = History_of_Anxiety))+
  scale_color_manual(values = c("#FAE367", "#768CCe", "#E7BCC6", "#B4BBC0"), limits = c("Yes", "No", "Refused", "Do not know")) +
  theme_linedraw()

```

The proportion of history of anxiety is relatively even across all ages. It remains below 25 percent. However, it is easy to see from the graph that the older the age, the lower the proportion. By age 65, the percentage had dropped to less than 12 percent. The prevalence of history of anxiety in 23- and 24-year-olds is a little higher than other age groups. Young people also shows sign of slightly higher variance compared other age groups in history of anxiety as well.

## Why smoking? Anxiety with frequency of smoking habits.

```{r}
nhisBar2 <- NHIS_final %>%
  filter(History_of_Anxiety !='Missing') %>%
  filter(Smoking !='Missing' & Smoking != 'Do not know' & Smoking!='Refused') 
nhisBar3 <- nhisBar2 %>%
  group_by(History_of_Anxiety,Smoking) %>%
  dplyr::summarise(Freq = n())
ggplot(nhisBar3, aes(x = Smoking, y=Freq, fill = History_of_Anxiety)) + 
    geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = c("#FAE367", "#768CCe", "#E7BCC6", "#B4BBC0"), limits = c("Yes", "No", "Refused", "Do not know")) +
  scale_x_discrete(limits = c("Every day", "Some days", "Not at all"))+
  theme_minimal()
```

According to our perceptions, smoking is a form of stress relief for some people who have just started smoking. Many smokers experience relief from anxiety after smoking. But is this true? The chart above divides the population into smokers and non-smokers and compares whether they have ever suffered from anxiety. About 27 percent of occasional smokers indicates a history of anxiety. About 22 percent of occasional smokers indicates a history of anxiety. About 19% of the never smokers indicate a history of anxiety. Looking at the graph, we can conclude that smokers are at least eight percent more likely to have anxiety disorders than non-smokers. We are not sure the causal relationship between smoking and anxiety, but it seems like a positive relationship exists between frequency of smoking and history of anxiety.

## Happier Work and Marriage: The Key to Reducing Anxiety?
```{r}
options(dplyr.summarise.inform = FALSE)
df$Marital_Status  <- factor(df$Marital_Status,c('Unmarried','Married') )
df$Marital_Status <- as.ordered(df$Marital_Status)

icecreamcolors <- c("#E7BCC6", "#768CCe")

counts2 <- df %>%
  group_by(Employment,Marital_Status,History_of_Anxiety) %>%
  summarize(Freq = sum(Freq))

vcd::mosaic(History_of_Anxiety ~ Employment + Marital_Status, counts2,
            direction = c("v", "v", "h"),
            highlighting_fill = icecreamcolors)
```

Mosaic plots are used for visualizing data from two or more qualitative variables to show their proportions or associations. Based on the plot above, we can see that people who are unmarried and unemployed are more likely to have Anxiety than other people. At the same time, people who are unemployed have slightly higher chance to be unmarried. Moreover, mosaic plot can also help check the independence of variables in dataset. Looking at the graph, we can see that the variables are possibly not independent to each other; there is no clear sign of “+” between each block.

## Geography and the LGBT+ Community: Variations in Anxiety Risk
```{r}
counts2 <- df %>%
  group_by(History_of_Anxiety,Sexual_Orientation,Region) %>%
  summarize(Freq = sum(Freq))

vcd::mosaic(History_of_Anxiety ~ Region + Sexual_Orientation, counts2,
            direction = c("h", "v", "h"),
            highlighting_fill = icecreamcolors)
```

Based on the plot, we can see that there is a lower concentration of LGBT+ individuals living in the southern and midwestern regions of the United States compared to other parts of the country. This may be due to a variety of factors, such as a lack of supportive communities or discrimination. However, the data also suggests that those who do live in the south and midwest are more likely to experience anxiety than those living in other regions. This could be a result of the challenges and barriers that they face in these areas, such as a lack of acceptance and support. Overall, this suggests that location can play a significant role in the mental health and well-being of LGBT+ individuals.

**Summary:**

We found that not all the factors we think of related to history of anxiety initially shown signs of correlation. In fact, from the loading plots, it’s interesting to find out only history of asthma are highly correlated with history of anxiety, others are less relevant by around 90 degrees of angle formed. Different age groups don’t indicate a huge difference in percent of anxiety as well. In conclusion, identity factors such as sex, sexual orientation, and social factors such as employment and marital status shown higher correlations with history of anxiety, others relationship remained in question and further testing.

<!--chapter:end:results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component
<iframe style="border-radius: 25px; border:none; background: #FDE6EC" src="interactiveHT.html" width="750" height="530"></iframe>

**Instructions:**
The interactive bar chart above shows the proportion of people indicate history of anxiety each year, breaking down by all the categorical variables (therefore excluded age). In general, it seems like people with other health issues shows a higher correlation with history of anxiety. Such conclusion is attained from ignoring the column “Do not know”, since such column usually contains too small of sample size therefore might not be as convincing to indicate a relationship.

Please feel free to click on any of the buttons at the top of the graph to explore the proportion break down by a specific group.


<!--chapter:end:interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion

**For data limitations:** 

The accuracy of survey results may be influenced by respondents’ willingness and ability to provide accurate and honest answers. People’s health and anxiety levels are subject to response bias, meaning that certain people or groups may respond to the survey more or less often. Minority groups’ response can also have effect on the behaviors of data since such groups are already in lower proportion of interviewees.
In summary, the above factors may affect the representativeness of the survey sample and may cause potentially bias the results.

**Lessons learned:** 

We have learned some lessons about conducting research and collecting data. We know the importance of having a clear research question and objectives, the need to carefully design and test survey questions, and the importance of considering potential limitations and challenges in the data collection and analysis. Moreover, through testing different factors (which we originally assume high relationship with dependent variable), we indeed found not all of them shows sign of correlation. This again enhanced our understanding of exploratory data; we don’t assume something and search for reason to back up such assumption, instead we would like to explore the data to have a higher understanding of our dataset.

**Future directions: **

For interactive components, we would like to be able to add several more plots and maps that show the geographical location, so that when people hover over the corresponding location, the other plots will change according to the data for that area. 

<!--chapter:end:conclusion.Rmd-->

