--- 
title: "NHIS Anxiety Analysis in Adults"
author: "Zhe Wang, Yingyi Zhu, Zixiao Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
--- 
title: "NHIS Anxiety Analysis in Adults"
author: "Zhe Wang, Yingyi Zhu, Zixiao Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction

In today's rapidly developing and competitive society, almost everyone has a certain degree of anxiety, which is manifested in a variety of mild or severe psychological diseases and behavioral symptoms. When it comes to school, we are afraid that we can not complete the study task well and get a bad result. When it comes to the job, we may doubt our abilities and fear not finding a job. When it comes to inquires from family and friends, we are also afraid of disappointing those who care about us. When it comes to interpersonal relationships, we often fear contact with strangers and worry that our language or behavior will suffer from the negative evaluation of others. These can be seen as signs of anxiety. We started studying this topic because we are also facing more or less stress nowadays. We often feel the negative emotions caused by anxiety. So what we want to see from the data is how anxiety affects our life and health or how it relates to each other. 

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Proposal
## Research topic

  Occasional anxiety is a normal part of life. Being a student at Columbia University, it's not uncommon to hear phrases such as being stressed about school work, midterms, and career searching. One news [article](https://www.who.int/news/item/02-03-2022-covid-19-pandemic-triggers-25-increase-in-prevalence-of-anxiety-and-depression-worldwide) from the **World Health Organization** even revealed that the prevalence of anxiety and depression has increased by 25% globally during the social environment of the COVID-19 pandemic. Furthermore, anxiety may interfere with daily activities, such as work performance, schoolwork, and relationships. Physical symptoms can include rapid heartbeat, tremors, breathlessness, and other symptoms such as upset stomach or nausea.

  For this exploratory data project, our team will look at a four-year NHIS data on 18-65 aged adults, focusing on the relationship between anxiety and other general factors such as gender and employment. Moreover, we will further our analysis by looking at other health factors like heart disease that could be correlated with feelings of anxiety.

## Data availability
  The [National Health Interview Survey](https://www.cdc.gov/nchs/nhis/data-questionnaires-documentation.htm)
 data we utilized was collected and processed by the National Center for Health
Statistics (NCHS). It is a cross-sectional household interview survey conducted through a geographic subgroup sampling technique (random selection), updated annually. The data contains statistical information on the interviewer's health status, health-related behaviors, and healthcare utilization history since 1993.

  We will limit our analysis to the recent years, 2018-2021 survey data only, and within the group
of 18-65 aged adults. The sample adult population of each year would be approximately 30,000. The data format we will be using will be CSV format. The total size over the four years adults data would be 112MB, including elders, which we would feature engineer later to exclude. We intended to import the CSV files to R studios by used the built-in read.csv(...) function call to conduct data cleaning and visualization of the relationship of anxiety between the following factors that were found in all four years of surveys: 

  For common independent factors, we have ages, years (split to Covid/non-Covid), marital status,
genders, races, sexual orientations, household numbers, regions, habits (such as smoking, alcohol, etc.), employment, history of chronic pains and hours of sleep. The list's order is random and does not have ranks of importance. We include these factors to help us understand our samples and the distribution of anxiety in the population, such as genders and regions. If the sample population distribution is highly imbalanced, we will thus adjust our strategies correspondingly by downsampling or upsampling.

  Additional to the common independent factors, we would further explore certain physical health
factors we found might be correlated: history of heart disease, history of cancer, history of stroke, history of diabetes, and history of asthma. Again, the order of the list above is random. We are interested in exploring the relationship between these above factors because many studies have shown mental health is correlated with physical health to different degrees. We would, therefore, like to examine the degree of correlation.

  One additional comment regarding our data is that it’s interview survey data, which are answered
without 100% truth guarantees. It’s possible the interviewees chose to give inaccurate information out of self-interest. Moreover, the health-related questions are also self-answered, which means there is not necessarily a formal background check to confirm. We don’t know if some health conditions have been cured. Therefore, we decided to use terms such as “history of anxiety” and “history of cancers” to adjust the level of accuracy.

  In summary, we will explore the relationship between anxiety(self-indicated or formally
diagnosed) with other factors, such as age, gender, and years, with a further focus on physical conditions. The NHIS data will help us achieve a four-year exploration with a rich sample adult population of around 30,000 each year. We will keep in mind the inaccuracy that comes with the nature of the NHIS data collection process.

Here is a link to the NHIS data: 
[National Health Interview Survey](https://www.cdc.gov/nchs/nhis/data-questionnaires-documentation.htm)

<!--chapter:end:proposal.Rmd-->


# Data 

Placeholder


## Sources
## Cleaning / transformation
## Missing value analysis

<!--chapter:end:data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

```{r}
library(dplyr)
library(tidyr)
library(grid)
library(ggplot2)
library(GGally)
library(ggalluvial)
```

**Percentage of interviewees with Anxiety Over 4 years, by gender**
```{r}
options(dplyr.summarise.inform = FALSE)
nhisBar <- NHIS_final %>%
  filter(History_of_Anxiety !='Missing') %>%
  filter(Sex=="Male" | Sex=="Female")
nhisBar1 <- nhisBar %>%
  group_by(Year, History_of_Anxiety, Sex) %>%
  dplyr::summarise(Freq = n())
ggplot(nhisBar1, aes(x = Year, y=Freq, fill = History_of_Anxiety)) + 
    geom_bar(position="fill", stat="identity") +
  facet_wrap(~Sex) +
  scale_fill_manual(values = c("#E7BCC6", "#768CCe", "#B4BBC0", "#FAE367")) +
  theme_minimal()
```

Although the population interviewed each year was not a fixed group of people, we have no way of knowing whether the same group of people had a change in their mental health during those years. However, according to the graph above, the percentage of interviewees with anxiety disorders has increased yearly—both the percentage of males and females. On the male side, we can see that the increase is relatively small, but there is no sign of a decrease. The increase from 2018 to 2019 is more significant on the female side. The increase is almost 50% of those with anxiety disorders in 2018. The increase continues each year slowly after that. 
We can also note that the proportion of women with anxiety disorders is greater than that of men, with almost 25% of women having anxiety disorders by 2021. 




<!--chapter:end:results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component



<!--chapter:end:interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion


<!--chapter:end:conclusion.Rmd-->

